Elephant Seal Age JAE Intraspecific Variation

### 2023-12-07 paper/paperv3.qmd
Little tweaks to the figure names and small edits to the text. Also updating the index to go to v3 of the paper

2.  Reproductive declines persist to the next generation (maternal effect senescence).

3.  Seal phenology is shifted later for older animals and breeders.

**Note**: *This paper is similar to another paper about polar bears (*Ursus maritimus*)* [@naciri2022].

@@

The model of Survival \~ Maternal age was significant before we treated Year as a random effect. Was that because pups born earlier in the study had more time to be seen again (i.e., a sampling artifact?) If so, the plot of the random effect of year should have a negative slope.

We also plotted survival bias to show that 95% of pups were resighted within 7 years. Both plots are supplemental.

plot_grid(year_ranef_plot, survival_bias_plot, nrow = 1, labels = "AUTO")

There is a drop off in recent years that seems to support the idea that recent years have a sampling bias, but the earlier portion suggests that overall the variation is caused by ocean conditions and not sampling. See the Cohort paper!

@@

We found that as maternal age increases, pup sex skews slightly towards males.

@@

#linear
pup_sex_mod <- glmer(is_male ~ age + (1 | animalID) + (1 | year),
                     data = pup_sex_data, 
                     family = "binomial")
summary(pup_sex_mod)

@@

>>>>

2.  Reproductive declines persist to the next generation (maternal effect senescence). That is, offspring survival and recruitment are decreased.

3.  Offspring sex ratios shift towards males with old age.

4.  Phenology is shifted later for older animals and breeders.

@@

@@

We found that as maternal age increases, pup sex skews slightly towards males (@fig-sex_ratio).

@@

#linear
pup_sex_mod <- glmer(is_male ~ age + (1 | animalID) + (1 | year),
                     data = pup_sex_data, 
                     family = "binomial")

@@

Supplemental figure for survival bias:

plot_grid(year_ranef_plot, survival_bias_plot, nrow = 1, labels = "AUTO")
```
